\large \textbf{Burrows-Wheeler transform for terabases}

### 2015-10-26 paper/paper.tex
Verification that the format exists.

We have implemented the proposed enhancements to the \BWT{} merging algorithm in a tool (\BWTmerge) intended for merging the \BWT{}s of large collections of short reads. \BWTmerge{} is written in C++, and the source code is available at GitHub.\footnote{\url{https://github.com/jltsiren/bwt-merge}} The implementation is built on top of the \emph{SDSL library} \cite{Gog2014b} and uses the features of C++11 extensively. As a result, it needs a fairly recent C++11 compiler to compile. We have built \BWTmerge{} on Linux and OS~X using g++.

@@

\end{itemize}
See Table~\ref{table:datasets} for further details on the datasets.

\smallbreak\noindent\textbf{Benchmarking.} For benchmarking with different parameter values, we converted four \BWT{} files (AA, TT, AT, and TA) containing a total of 1.49~Tbp from the \RS{} dataset to the native format used by \BWTmerge. Then we merged the \BWT{}s (in the given order). We used 128~MB or 256~MB run buffers and 256~MB or 512~MB thread buffers. The number of merge buffers was 4 or 5 with 512~MB thread buffers and 5 or 6 with 256~MB thread buffers, so that the files on disk were always merged from either 8~GB or 16~GB of thread buffers.

>>>>

We have implemented the improved \BWT{} merging algorithm as a tool for merging the \BWT{}s of large collections of short reads. The tool, \BWTmerge{}, is written in C++, and the source code is available at GitHub.\footnote{\url{https://github.com/jltsiren/bwt-merge}} The implementation is built on top of the \emph{SDSL library} \cite{Gog2014b} and uses the features of C++11 extensively. As a result, it needs a fairly recent C++11 compiler to compile. We have successfully built \BWTmerge{} on Linux and OS~X using g++.

@@

\end{itemize}
See Table~\ref{table:datasets} for further details on the datasets. We used a development version of \BWTmerge{} that was essentially equivalent to v0.3 for the experiments. For the other tools, we used the versions that were available on GitHub in October~2015.

\smallbreak\noindent\textbf{Benchmarking.} For benchmarking with different parameter values, we converted four \BWT{} files (AA, TT, AT, and TA) containing a total of 1.49~Tbp from the \RS{} dataset to the \emph{native format} of \BWTmerge. This format includes the \BWT{} and the \rank/\select{} structures required by the FM-index. We then merged the \BWT{}s (in the given order). We used 128~MB or 256~MB run buffers and 256~MB or 512~MB thread buffers. The number of merge buffers was 4 or 5 with 512~MB thread buffers and 5 or 6 with 256~MB thread buffers, so that the files on disk were always merged from either 8~GB or 16~GB of thread buffers.
